---
title: "Isolines"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Isolines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = nzchar(Sys.getenv("COMPILE_VIG"))
)
```

```{r setup}
library(ggplot2)
library(VancouvR)
```

The City of Vancouver Open Data Portal includes an elevation contour dataset with 1-metre contour lines covering the city. Because the dataset has a `geo_shape` field, `get_cov_data()` downloads it as [FlatGeobuf](https://flatgeobuf.org) and returns an `sf` object with its coordinate reference system already set, so it can be passed directly to `geom_sf()` without any additional conversion.

```{r}
contours <- get_cov_data("elevation-contour-lines-1-metre-contours")
class(contours)  # "sf" "data.frame"
```

Mapping the contour lines coloured by elevation takes only a few lines:

```{r}
ggplot(contours) +
  geom_sf(aes(color=elevation), size=0.1) +
  scale_color_viridis_c(option="inferno", guide="none") +
  theme_void()
```

The same pattern works for any spatial dataset on the portal. Use `get_cov_metadata()` to check whether a dataset has a `geo_shape` field before downloading:

```{r}
get_cov_metadata("elevation-contour-lines-1-metre-contours") |>
  dplyr::filter(type == "geo_shape")
```

To find spatial datasets in the first place, filter the catalogue on the `geo` feature:

```{r}
list_cov_datasets(refine = "features:geo") |>
  dplyr::select(dataset_id, title)
```

